The necessity of hypermedia RDF and an approach to achieve it

### 2012-03-01 eswc-2012/workshop2.tex
grammar...
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@145 43ef1190-90fd-4dd7-a769-d0121f02b80e
gregg gone
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@146 43ef1190-90fd-4dd7-a769-d0121f02b80e

We also note that some bloggers in the developer community, see
e.g. a post by Gregg
Caines\footnote{\url{http://caines.ca/blog/programming/the-sun-is-setting-on-rails-style-mvc-frameworks/}},
%\cite{sunsetonmvc} 
is currently predicting a paradigm shift in common practices, prompted
by the trend towards richer clients. This has caused a departure from
the time-tested Model-View-Controller pattern that has been the
dominant paradigm in web development for more than a decade.

Semantic Web services is likely to be an important source of data for
future applications, but for foreseeable future just one of many. A
key promise of Linked Open Data (LOD) in particular, and the Semantic
Web in general is the ability to integrate many data sources
easily. There are two key issues, first read-write operations must be
similar to how it is done with other hypermedia types to make it
possible to use generic code to minimize the effort required to
support RDF. Secondly, it requires relevant links and that the
resulting graph can be traversed by reasonable means.

>>>>

Semantic Web services are likely to be an important source of data for
future applications, but for foreseeable future just one of many. A
key promise of Linked Open Data (LOD) in particular, and the Semantic
Web in general is the ability to integrate many data sources
easily. There are two key issues, first read-write operations must be
similar to how it is done with other hypermedia types to make it
possible to use generic code to minimize the effort required to
support RDF. Secondly, it requires relevant links and that the
resulting graph can be traversed by reasonable means.
